Subgroup cost analysis

### 2020-09-21 src/eba_sims_w_data.Rmd
Update to most recent

q <- seq(0, 0.031, 0.031/1000)
x <- seq(1, 1.5, 1/10000)
adjustments <- sort(round(rtruncnorm(n=length(q), a=1, b=1.5, mean=1.1, sd=0.1), digits = 4))
E.matrix <- matrix(, nrow = 1001, ncol = 1001)
Pm <- 2
Pd <- 60 # from Satu
rl <- 0
Fn = 0.259 # Vuosikertomus 2019
qalt <- seq(0, 0.06, 0.06/1000) # Larger q
q <- seq(0, 0.031, 0.031/1000) # from data
for(i in 1:1001){
  Fratio <- adjustments[i] / (1 + Fn * (adjustments[i] - 1))
  for(j in 1:1001){
    Em <- Pm * (Fratio - 1 - q[j] * rl)
    Ed <- Pd * q[j]
    E.matrix[i, j] <- Em - Ed
    }
}

@@

```{r}
colnames(E.long) <- c("adjustment", "q", "cost")
ggplot(E.long, aes(x = q, y = adjustment, z = cost)) +
geom_tile(aes(fill=cost)) +
  stat_contour(color = "white", size = 0.7, bins = 2) +
  scale_fill_gradientn(colours=c("blue", "red")) +
labs(x="q%", y="Adjustment", title="Cost surface", subtitle = paste0("Surface minimum: ", round(min(E.long$cost), 2), ". Cost effect thresholds highlighted at 0 and -1 euros.")) +
theme_bw() +
scale_x_continuous(breaks = c(1, 1001), labels = c("0", "3.1")) +
scale_y_continuous(breaks = c(1, 1001), labels = c(as.character(min(adjustments)), as.character(max(adjustments))))
```

>>>>

q <- seq(0, 0.032, 0.032/1000)
adjustments <- seq(1, 2, 1/1000)
E.matrix <- matrix(, nrow = 1001, ncol = 1001)
Pm <- 2
Pd <- 60 # from Satu
rl <- 0
Fn = 0.1066 # Data
for(i in 1:1001){
  Fratio <- adjustments[i] / (1 + Fn * (adjustments[i] - 1))
  for(j in 1:1001){
    Em <- Pm * (Fratio - 1 - q[j] * rl)
    Ed <- Pd * q[j]
    E.matrix[i, j] <- Em - Ed
    }
}

@@

```{r}
colnames(E.long) <- c("adjustment", "q", "cost")
ggplot(E.long, aes(x = q, y = adjustment, z = cost)) +
geom_tile(aes(fill=cost)) +
  stat_contour(color = "white", size = 0.7, bins = 2) +
  scale_fill_gradientn(colours=c("blue", "red")) +
labs(x="q%", y="Adjustment", title="Cost surface (2018-2020)", subtitle = paste0("Surface minimum: ", round(min(E.long$cost), 2), ". Cost effect thresholds highlighted at 0 and -1 euros.", "\n", "Dots mark current model performance with a 6 or 12 month extension strategy.")) + 
  annotate("point", x = 800, y = which(adjustments > 1.3619 & adjustments < (1.3619 + 0.001)), colour = "white", size = 2, alpha = 1) +
  annotate("point", x = 800, y = which(adjustments > 1.9749 & adjustments < (1.9749 + 0.001)), colour = "white", size = 2, alpha = 1) +
  annotate("text", x = 760, y = which(adjustments > 1.3619 & adjustments < (1.3619 + 0.001)), label = "6", colour = "white") +
  annotate("text", x = 760, y = which(adjustments > 1.9749 & adjustments < (1.9749 + 0.001)), label = "12", colour = "white") +
theme_bw() +
scale_x_continuous(breaks = c(1, 1001), labels = c("0", "3.2")) +
scale_y_continuous(breaks = c(1, 1001), labels = c(as.character(min(adjustments)), as.character(max(adjustments))))
```

### 2020-09-21 src/subgroup_analysis.Rmd
Update to most recent

@@

## Windowing
```{r windowing}
# Windowing between 2018-2020
wfU30don <- subset(fU30don, date >= "2018-01-01" & date <= "2019-12-30")
wfU30def <- subset(fU30Hbdeferred, date >= "2018-01-01" & date <= "2019-12-30")

@@

>>>>

# Women 18-25
f25Hbdeferred <- filter_donations(data = donation10, donat_phleb = "*", gender = "Women", age = c(17, 26), Hb_deferral = 1)
f25don <- filter_donations(data = donation10, donat_phleb = "K", gender = "Women", status = "-", age = c(17, 26))

@@

## Windowing
```{r windowing}
# Windowing between 2018-2020
wf25don <- subset(f25don, date >= "2018-01-01" & date <= "2019-12-30")
wf25def <- subset(f25Hbdeferred, date >= "2018-01-01" & date <= "2019-12-30")

wfU30don <- subset(fU30don, date >= "2018-01-01" & date <= "2019-12-30")
wfU30def <- subset(fU30Hbdeferred, date >= "2018-01-01" & date <= "2019-12-30")

@@

# Extra strategy
```{r tallyingExtra}
vec <- c()
defvec <- c()
for(i in 1:10000){
  # Get donor and date
  donor <- wf25don$donor[i]
  dondate <- as.Date(head(wf25don$date[i], 10))

  # Get donor window
  yearw <- subset(wf25don, date >= dondate & date <= (dondate + years(1)))
  defyearw <- subset(wf25def, date >= dondate & date <= (dondate + years(1)))

# Reinstance p
p <- nrow(wf25don)/nrow(wdons)
p
```

```{r dons_lostExtra}
# All donations lost if interval extended (%)
vec[is.na(vec)] <- 0
subflux_effect <- sum(vec[vec > 1] - 1)/sum(vec)
dons_lost <- subflux_effect * p
dons_lost
```

```{r deferreals_avoidedExtra}
# Deferrals avoided if interval extended (%)
defvec[is.na(defvec)] <- 0
sub_avoided <- sum(defvec)/sum(vec)
def_avoided <- sub_avoided * p
def_avoided
```

```{r cost_effectExtra}
E <- 2*dons_lost - 60*def_avoided
E
```
